---
title: "PRECISE open trial: analysis code"
subtitle: "Preliminary Effects of PRECISE, a Personalized and Idiographically-Tailored Adjunctive Intervention, on Suicidal Ideation and Psychiatric Symptoms in Young Adults"
author: "Kevin S. Kuehn, PhD"
date: "Rendered `r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: false
    df_print: kable
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE,
                      fig.width = 8, fig.height = 4, dpi = 150)
options(knitr.kable.NA = "", digits = 4)
```

This document contains the analysis code for the manuscript. All results are
computed from the item-level, de-identified datasets in `data/`: scale scoring,
descriptive tables, the Bayesian multilevel models, the responder analysis, and
the EMA compliance, missingness and safety summaries.

| Manuscript element | Data file |
|---|---|
| Table 1 (demographics) | `precise_demographics.csv` |
| Table 2 (acceptability, feasibility, usability) | `precise_implementation.csv` |
| EMA compliance, missingness models, EMA safety counts | `precise_ema.csv` |
| Table 4 and Figure 2 (Bayesian multilevel models) | `precise_visits.csv` |
| Table 5 (≥50% responders) | `precise_visits.csv` |

Figure 1 (CONSORT), Table 3 (session attendance), treatment fidelity and the
adverse-event log are summarized from study tracking records and are not
computed here.

The first knit compiles and samples seven Stan models (roughly 10 minutes);
fitted models are cached in `fits/` so later knits take seconds. Delete `fits/`
to refit from scratch.

```{r packages}
library(dplyr)
library(tidyr)
library(readr)
library(ggplot2)
library(brms)
library(bayestestR)
library(lme4)

options(mc.cores = min(4, parallel::detectCores()))
SEED <- 20260917
dir.create("fits", showWarnings = FALSE)

tp_levels <- c("baseline", "week6", "week12")
tp_labels <- c("Baseline", "6 weeks", "12 weeks")
```

# Data

```{r data}
visits <- read_csv("data/precise_visits.csv", show_col_types = FALSE) %>%
  mutate(timepoint = factor(timepoint, levels = tp_levels))
implementation <- read_csv("data/precise_implementation.csv", show_col_types = FALSE)
demographics   <- read_csv("data/precise_demographics.csv", show_col_types = FALSE)
ema            <- read_csv("data/precise_ema.csv", show_col_types = FALSE)
promis_par     <- read_csv("data/promis_item_parameters.csv", show_col_types = FALSE)

visits %>% count(timepoint, name = "n participants") %>% knitr::kable()
```

# Scale scoring

```{r scoring-helpers}
# Sum score requiring a minimum proportion of answered items; missing items are
# replaced by the person's mean of answered items (prorated sum).
prorated_sum <- function(items, min_prop = 0.8) {
  n_ok <- rowSums(!is.na(items))
  out <- rowMeans(items, na.rm = TRUE) * ncol(items)
  out[n_ok < ceiling(min_prop * ncol(items))] <- NA
  out
}

# Expected a posteriori (EAP) theta under the graded response model with a
# standard normal prior, using fixed (published) item parameters.
#   resp: matrix of responses coded 1..5 (rows = people, columns = items)
#   par:  data frame with one row per item: a, b1..b4
grm_eap <- function(resp, par, nodes = seq(-6, 6, length.out = 241)) {
  stopifnot(ncol(resp) == nrow(par))
  prior <- dnorm(nodes)
  b <- as.matrix(par[, c("b1", "b2", "b3", "b4")])
  apply(resp, 1, function(r) {
    answered <- which(!is.na(r))
    if (!length(answered)) return(NA_real_)
    lik <- prior
    for (j in answered) {
      # cumulative P(X >= k) for k = 1..6, i.e. 1, P*(b1), ..., P*(b4), 0
      p_star <- cbind(1, plogis(par$a[j] * outer(nodes, b[j, ], "-")), 0)
      lik <- lik * (p_star[, r[j]] - p_star[, r[j] + 1])
    }
    sum(nodes * lik) / sum(lik)
  })
}
promis_t <- function(data, bank, min_items) {
  par  <- promis_par %>% filter(.data$bank == .env$bank) %>% arrange(position)
  resp <- as.matrix(data[, par$item_id])
  t <- 50 + 10 * grm_eap(resp, par)
  t[rowSums(!is.na(resp)) < min_items] <- NA   # < 80% of items answered
  t
}
```

```{r scoring}
item <- function(prefix, k, width = 2) sprintf(paste0(prefix, "_%0", width, "d"), k)

# CERQ: nine 4-item subscales (items k, k+9, k+18, k+27), items scored 1-5
cerq_key <- list(
  self_blame = c(1, 10, 19, 28), acceptance = c(2, 11, 20, 29),
  rumination = c(3, 12, 21, 30), positive_refocusing = c(4, 13, 22, 31),
  refocus_on_planning = c(5, 14, 23, 32), positive_reappraisal = c(6, 15, 24, 33),
  putting_into_perspective = c(7, 16, 25, 34), catastrophizing = c(8, 17, 26, 35),
  other_blame = c(9, 18, 27, 36))
cerq_adaptive <- unlist(cerq_key[c("acceptance", "positive_refocusing", "refocus_on_planning",
                                   "positive_reappraisal", "putting_into_perspective")])
cerq_maladaptive <- unlist(cerq_key[c("self_blame", "rumination", "catastrophizing", "other_blame")])

scores <- visits %>%
  mutate(
    # MSSI: items 5-18 are administered only after a positive screen on items
    # 1-4, so unadministered items contribute 0 to the total (range 0-54).
    # CSES: REDCap response options were coded 1-10, so totals range 26-260.
    mssi = rowSums(across(all_of(item("mssi", 1:18))), na.rm = TRUE),
    cerq_adaptive    = prorated_sum(across(all_of(item("cerq", cerq_adaptive)))),
    cerq_maladaptive = prorated_sum(across(all_of(item("cerq", cerq_maladaptive)))),
    cses             = prorated_sum(across(all_of(item("cses", 1:26)))),
    promis_dep = promis_t(visits, "depression", min_items = 23),
    promis_anx = promis_t(visits, "anxiety",    min_items = 24)
  ) %>%
  select(id, timepoint, cssrs, mssi, cerq_adaptive, cerq_maladaptive, cses, promis_dep, promis_anx)
```

Item-level missingness is minimal, so the 80% completion rules never exclude a
visit:

```{r missing-items}
tibble(
  measure = c("MSSI screening items (1-4)", "CERQ", "CSES", "PROMIS Depression", "PROMIS Anxiety"),
  `missing item responses` = c(
    sum(is.na(visits[, item("mssi", 1:4)])), sum(is.na(visits[, item("cerq", 1:36)])),
    sum(is.na(visits[, item("cses", 1:26)])),
    sum(is.na(visits[, grep("^EDDEP", names(visits))])),
    sum(is.na(visits[, grep("^EDANX", names(visits))]))),
  `visits scored` = c(sum(!is.na(scores$mssi)), sum(!is.na(scores$cerq_adaptive)),
                      sum(!is.na(scores$cses)), sum(!is.na(scores$promis_dep)),
                      sum(!is.na(scores$promis_anx)))
) %>% knitr::kable()
```

Observed means (SD) by visit:

```{r observed-means}
outcomes <- tribble(
  ~var,               ~label,
  "cssrs",            "CSSRS",
  "mssi",             "MSSI",
  "cerq_adaptive",    "CERQ Adaptive (composite)",
  "cerq_maladaptive", "CERQ Maladaptive (composite)",
  "cses",             "CSES (coping self-efficacy)",
  "promis_dep",       "PROMIS Depression (T-score)",
  "promis_anx",       "PROMIS Anxiety (T-score)")

scores_long <- scores %>%
  pivot_longer(-c(id, timepoint), names_to = "var", values_to = "y") %>%
  mutate(var = factor(var, levels = outcomes$var, labels = outcomes$label))

scores_long %>%
  group_by(Outcome = var, timepoint) %>%
  summarise(n = sum(!is.na(y)),
            `M (SD)` = sprintf("%.2f (%.2f)", mean(y, na.rm = TRUE), sd(y, na.rm = TRUE)),
            .groups = "drop") %>%
  pivot_wider(names_from = timepoint, values_from = c(n, `M (SD)`), names_vary = "slowest") %>%
  knitr::kable()
```

# Table 1. Baseline demographic characteristics

`precise_demographics.csv` is not linkable to the outcome files and each column
was permuted independently before release, so marginal distributions (all that
Table 1 reports) are exact but rows do not describe real individuals.

```{r table1}
cont_row <- function(x, label) {
  tibble(Characteristic = label, n = NA_integer_,
         `%` = sprintf("M (SD) = %.2f (%.2f); median (range) = %.1f (%d–%d)",
                       mean(x), sd(x), median(x), min(x), max(x)))
}
cat_rows <- function(x, label) {
  tab <- sort(table(x), decreasing = TRUE)
  bind_rows(tibble(Characteristic = label, n = NA_integer_, `%` = ""),
            tibble(Characteristic = paste0(" ", names(tab)), n = as.integer(tab),
                   `%` = sprintf("%.1f%%", 100 * as.integer(tab) / length(x))))
}
bind_rows(
  cont_row(demographics$age, "Age, years"),
  cat_rows(demographics$sex_at_birth, "Sex assigned at birth"),
  cat_rows(demographics$gender_identity, "Gender identity"),
  cat_rows(demographics$race_ethnicity, "Race/Ethnicity"),
  cat_rows(demographics$hispanic_latino, "Hispanic, Latino, Spanish, or Mexican origin"),
  cont_row(demographics$education_years, "Education, years"),
  cat_rows(demographics$current_student, "Current student"),
  cat_rows(demographics$employment, "Employment status"),
  cat_rows(demographics$relationship, "Relationship status")
) %>% knitr::kable(caption = "Table 1. Baseline demographic characteristics (N = 30).")
```

# Table 2. Feasibility and acceptability

```{r table2}
sus_items <- as.matrix(implementation[, item("sus", 1:10)])
odd <- seq(1, 9, 2); even <- seq(2, 10, 2)
imp <- implementation %>%
  transmute(id,
            AIM = rowSums(across(aim_1:aim_4)),
            IAM = rowSums(across(iam_1:iam_4)),
            FIM = rowSums(across(fim_1:fim_4)),
            SUS = 2.5 * (rowSums(sus_items[, odd] - 1) + rowSums(5 - sus_items[, even])))

fmt_range <- function(x) sprintf("%s (%s–%s)", format(median(x), nsmall = 1),
                                 format(min(x)), format(max(x)))
tibble(
  Measure = c("AIM — Acceptability", "IAM — Appropriateness", "FIM — Feasibility", "SUS — Usability"),
  `Scale range` = c("4–20", "4–20", "4–20", "0–100"),
  N = nrow(imp),
  `Total M (SD)` = sapply(imp[-1], function(x) sprintf("%.2f (%.2f)", mean(x), sd(x))),
  `Item-level M (SD)` = c(sapply(imp[c("AIM", "IAM", "FIM")],
                                 function(x) sprintf("%.2f (%.2f)", mean(x / 4), sd(x / 4))), "—"),
  `Median (range)` = sapply(imp[-1], fmt_range)
) %>% knitr::kable(caption = "Table 2. Feasibility and acceptability of PRECISE at post-treatment.")
```

```{r table2-text}
n_imp <- nrow(imp)
pct <- function(k, n) sprintf("%d/%d (%.1f%%)", k, n, 100 * k / n)
tibble(
  Statistic = c("Below scale midpoint (12) on AIM, IAM or FIM",
                "Maximum rating (20): AIM", "Maximum rating (20): IAM", "Maximum rating (20): FIM",
                "SUS at or above 68 (above-average usability)",
                "SUS at or above 85 (excellent)",
                "Three lowest SUS scores"),
  Value = c(pct(sum(imp$AIM < 12 | imp$IAM < 12 | imp$FIM < 12), n_imp),
            pct(sum(imp$AIM == 20), n_imp), pct(sum(imp$IAM == 20), n_imp), pct(sum(imp$FIM == 20), n_imp),
            pct(sum(imp$SUS >= 68), n_imp), pct(sum(imp$SUS >= 85), n_imp),
            paste(sort(imp$SUS)[1:3], collapse = ", "))
) %>% knitr::kable()

round(cor(imp[-1]), 2) %>% knitr::kable(caption = "Pearson correlations among implementation measures.")
```

# EMA compliance and missingness

`precise_ema.csv` has one row per scheduled prompt: 30 participants × 42 days ×
5 prompts. `completed` is 1 when a completed survey was submitted for that
prompt.

```{r ema-compliance}
by_person <- ema %>% group_by(ema_id) %>% summarise(rate = mean(completed), .groups = "drop")
tibble(
  `Scheduled prompts` = nrow(ema),
  `Completed surveys` = sum(ema$completed),
  `Overall compliance` = sprintf("%.1f%%", 100 * mean(ema$completed)),
  `Per-participant M (SD)` = sprintf("%.1f%% (%.2f%%)", 100 * mean(by_person$rate), 100 * sd(by_person$rate)),
  `Per-participant range` = sprintf("%.1f%%–%.1f%%", 100 * min(by_person$rate), 100 * max(by_person$rate))
) %>% knitr::kable()
```

```{r ema-compliance-fig, fig.height = 3.2}
bind_rows(
  ema %>% group_by(x = (study_day - 1) %/% 7 + 1) %>% summarise(rate = mean(completed)) %>%
    mutate(panel = "Study week"),
  ema %>% group_by(x = ping) %>% summarise(rate = mean(completed)) %>%
    mutate(panel = "Prompt within day")
) %>%
  ggplot(aes(x, rate)) +
  geom_col(fill = "#3B6FA0", width = 0.7) +
  facet_wrap(~ panel, scales = "free_x") +
  scale_x_continuous(breaks = 1:6) +
  scale_y_continuous(labels = scales::percent, limits = c(0, 1), expand = c(0, 0)) +
  labs(x = NULL, y = "Prompts completed") +
  theme_minimal(base_size = 11) +
  theme(panel.grid.major.x = element_blank(), panel.grid.minor = element_blank())
```

## Predictors of a missed prompt

Frequentist logistic mixed-effects models with a random intercept for
participant. Lagged predictors come from the immediately preceding scheduled
prompt (within participant) and are therefore only defined when that prompt was
completed. Negative emotion is the mean of the five 0–100 items (sad, angry,
afraid, ashamed, guilty), standardised.

```{r ema-missingness}
ema_m <- ema %>%
  mutate(neg_emotion = rowMeans(across(c(anger, shame, sad, fear, guilt)))) %>%
  arrange(ema_id, study_day, ping) %>%
  group_by(ema_id) %>%
  mutate(missed   = 1L - completed,
         prior_na = lag(neg_emotion),
         prior_si = lag(si_any)) %>%
  ungroup() %>%
  mutate(day_wk = (study_day - 1) / 7,                    # per study week
         prior_na_z = as.numeric(scale(prior_na)))

ctrl <- glmerControl(optimizer = "bobyqa")
m_time <- glmer(missed ~ day_wk + ping + (1 | ema_id), data = ema_m, family = binomial, control = ctrl)
m_na   <- glmer(missed ~ day_wk + ping + prior_na_z + (1 | ema_id), data = ema_m, family = binomial, control = ctrl)
m_si   <- glmer(missed ~ day_wk + ping + prior_si + (1 | ema_id), data = ema_m, family = binomial, control = ctrl)

tidy_glmer <- function(m, model) {
  co <- coef(summary(m))
  tibble(Model = model, Term = rownames(co), b = co[, 1], SE = co[, 2],
         OR = exp(co[, 1]), p = co[, 4], `n prompts` = nobs(m))
}
bind_rows(tidy_glmer(m_time, "Time only"),
          tidy_glmer(m_na, "+ prior negative emotion"),
          tidy_glmer(m_si, "+ prior suicidal ideation")) %>%
  filter(Term != "(Intercept)") %>%
  mutate(Term = recode(Term, day_wk = "Study week", ping = "Prompt number within day",
                       prior_na_z = "Negative emotion at prior prompt (z)",
                       prior_si = "Suicidal/self-harm thoughts at prior prompt"),
         across(c(b, SE, OR), ~ round(.x, 3)), p = format.pval(p, digits = 2, eps = 0.001)) %>%
  knitr::kable()
```

# EMA safety summary

```{r ema-safety}
done <- ema %>% filter(completed == 1)
n_done <- nrow(done)
count_row <- function(label, flag) {
  flag <- coalesce(flag, FALSE)
  tibble(Event = label, Surveys = sum(flag),
         `% of completed surveys` = sprintf("%.1f%%", 100 * sum(flag) / n_done),
         Participants = n_distinct(done$ema_id[flag]))
}
bind_rows(
  count_row("Thoughts of hurting or killing self since last prompt", done$si_any == 1),
  count_row("Self-harm or suicide attempt in past 30 minutes", done$selfharm_30m == 1),
  count_row("Any suicidal intent in past 30 minutes", done$intent_suicide_30m >= 1),
  count_row("Current intent: none", done$intent_suicide_now == 0),
  count_row("Current intent: a little (brief thoughts, no intent)", done$intent_suicide_now == 1),
  count_row("Current intent: moderate (thoughts, no intent)", done$intent_suicide_now == 2),
  count_row("Current intent: a lot / severe (planning or specific plan)", done$intent_suicide_now >= 3)
) %>% knitr::kable()

done %>% filter(intent_suicide_now == 2) %>% count(ema_id, sort = TRUE) %>%
  summarise(`Surveys with moderate current intent` = sum(n),
            `From the single highest-reporting participant` = max(n)) %>%
  knitr::kable()
```

# Bayesian multilevel models (Table 4)

Each outcome is modelled as `y ~ timepoint + (1 | id)` with a Gaussian
likelihood: time is a categorical fixed effect (baseline as reference) and
participants have random intercepts. Weakly informative priors are placed on
the two change coefficients and on the between-person SD: Normal(0, 10) and
Student-t(3, 0, 5) for every outcome except the CSES, whose 26–260 range calls
for Normal(0, 50) and Student-t(3, 0, 20). The intercept and residual SD keep
the `brms` defaults. Sampling: 4 chains × 3,000 iterations (1,000 warm-up) =
8,000 posterior draws.

```{r model-spec}
model_spec <- tribble(
  ~var,               ~prior_b,           ~prior_sd,
  "cssrs",            "normal(0, 10)",    "student_t(3, 0, 5)",
  "mssi",             "normal(0, 10)",    "student_t(3, 0, 5)",
  "cerq_adaptive",    "normal(0, 10)",    "student_t(3, 0, 5)",
  "cerq_maladaptive", "normal(0, 10)",    "student_t(3, 0, 5)",
  "cses",             "normal(0, 50)",    "student_t(3, 0, 20)",
  "promis_dep",       "normal(0, 10)",    "student_t(3, 0, 5)",
  "promis_anx",       "normal(0, 10)",    "student_t(3, 0, 5)"
) %>% left_join(outcomes, by = "var")

model_spec %>% select(Outcome = label, `Prior: change coefficients` = prior_b,
                      `Prior: between-person SD` = prior_sd) %>% knitr::kable()
```

```{r fit-models, results = "hide"}
fit_outcome <- function(var, prior_b, prior_sd) {
  d <- scores %>% select(id, timepoint, y = all_of(var)) %>% filter(!is.na(y))
  brm(y ~ timepoint + (1 | id), data = d, family = gaussian(),
      prior = c(set_prior(prior_b, class = "b"), set_prior(prior_sd, class = "sd")),
      chains = 4, iter = 3000, warmup = 1000, seed = SEED,
      control = list(adapt_delta = 0.95), refresh = 0,
      file = file.path("fits", var), file_refit = "on_change")
}
fits <- Map(fit_outcome, model_spec$var, model_spec$prior_b, model_spec$prior_sd)
```

```{r summarise-models}
summarise_fit <- function(fit, label, effect_size = FALSE) {
  draws <- as_draws_df(fit)
  y_sd  <- sd(fit$data$y)
  rhat  <- rhat(fit)
  pooled_sd <- sqrt(draws$sd_id__Intercept^2 + draws$sigma^2)
  one <- function(par, timepoint, change) {
    x <- draws[[par]]
    out <- tibble(Outcome = label, Timepoint = timepoint,
                  Estimate = median(x), lower = quantile(x, .025), upper = quantile(x, .975),
                  pd = NA_real_, rope = NA_real_, Rhat = rhat[[par]], es = NA_character_)
    if (change) {
      out$pd   <- 100 * as.numeric(p_direction(x))
      out$rope <- 100 * as.numeric(rope(x, range = c(-0.1, 0.1) * y_sd, ci = 1))
      if (effect_size) {
        d <- x / pooled_sd
        out$es <- sprintf("%.2f [%.2f, %.2f]", median(d), quantile(d, .025), quantile(d, .975))
      }
    }
    out
  }
  bind_rows(one("b_Intercept", "Intercept (Baseline)", FALSE),
            one("b_timepointweek6", "6-week change", TRUE),
            one("b_timepointweek12", "12-week change", TRUE))
}

table4 <- bind_rows(Map(summarise_fit, fits, model_spec$label,
                        model_spec$var %in% c("cssrs", "mssi")))

table4 %>%
  transmute(Outcome, Timepoint,
            Estimate = sprintf("%.2f", Estimate),
            `95% CrI` = sprintf("[%.2f, %.2f]", lower, upper),
            pd = ifelse(is.na(pd), "–", sprintf("%.2f%%", pd)),
            `% in ROPE` = ifelse(is.na(rope), "–", sprintf("%.2f%%", rope)),
            Rhat = sprintf("%.3f", Rhat),
            `ES [95% CrI]` = coalesce(es, "")) %>%
  knitr::kable(caption = "Table 4. Posterior estimates for change from baseline to 6- and 12-week follow-up. Estimate = posterior median; pd = probability of direction; ROPE = ±0.1 SD of the outcome; ES = change divided by the model-implied pooled SD, sqrt(between-person variance + residual variance).")
```

Convergence and sampling diagnostics across all parameters of each model:

```{r diagnostics}
bind_rows(lapply(names(fits), function(v) {
  s <- posterior::summarise_draws(as_draws_df(fits[[v]]), "rhat", "ess_bulk", "ess_tail")
  s <- s[!grepl("^(r_id|lp__|lprior)", s$variable), ]
  tibble(Outcome = outcomes$label[outcomes$var == v], `n obs` = nobs(fits[[v]]),
         `max Rhat` = round(max(s$rhat), 3), `min bulk ESS` = round(min(s$ess_bulk)),
         `min tail ESS` = round(min(s$ess_tail)),
         `divergent transitions` = sum(nuts_params(fits[[v]], pars = "divergent__")$Value))
})) %>% knitr::kable()
```

# Figure 2. Model-estimated trajectories of suicidal ideation

```{r figure2, fig.width = 7.5, fig.height = 3.6}
estimated_means <- function(fit, label) {
  d <- as_draws_df(fit)
  m <- cbind(d$b_Intercept, d$b_Intercept + d$b_timepointweek6, d$b_Intercept + d$b_timepointweek12)
  tibble(Outcome = label, timepoint = factor(tp_labels, levels = tp_labels),
         mean = apply(m, 2, median), lower = apply(m, 2, quantile, .025),
         upper = apply(m, 2, quantile, .975))
}
fig2 <- bind_rows(estimated_means(fits$cssrs, "CSSRS ideation severity (0–5)"),
                  estimated_means(fits$mssi, "MSSI total (0–54)"))

ggplot(fig2, aes(timepoint, mean, group = 1)) +
  geom_line(colour = "#3B6FA0", linewidth = 0.8) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.08, colour = "#3B6FA0") +
  geom_point(size = 2.6, colour = "#3B6FA0") +
  facet_wrap(~ Outcome, scales = "free_y") +
  expand_limits(y = 0) +
  labs(x = NULL, y = "Model-estimated mean (95% CrI)") +
  theme_minimal(base_size = 11) +
  theme(panel.grid.minor = element_blank(), strip.text = element_text(face = "bold"))

fig2 %>% mutate(across(c(mean, lower, upper), ~ round(.x, 2))) %>% knitr::kable()
```

# Table 5. Clinically meaningful response (≥50% reduction from baseline)

A relative reduction is undefined for a baseline score of 0, so those
participants are excluded from that measure's responder analysis.

```{r table5}
responders <- scores %>%
  select(id, timepoint, CSSRS = cssrs, MSSI = mssi) %>%
  pivot_longer(c(CSSRS, MSSI), names_to = "Measure", values_to = "y") %>%
  group_by(id, Measure) %>%
  mutate(baseline = y[timepoint == "baseline"]) %>%
  ungroup() %>%
  filter(timepoint != "baseline", !is.na(y), baseline > 0) %>%
  group_by(Measure, timepoint) %>%
  summarise(n = n(), k = sum(y <= 0.5 * baseline), .groups = "drop") %>%
  mutate(responders = sprintf("%d (%.1f%%)", k, 100 * k / n)) %>%
  select(-k) %>%
  pivot_wider(names_from = timepoint, values_from = c(n, responders), names_vary = "slowest")

responders %>%
  rename(`n (6-week)` = n_week6, `≥50% responders, 6-week` = responders_week6,
         `n (12-week)` = n_week12, `≥50% responders, 12-week` = responders_week12) %>%
  knitr::kable(caption = "Table 5. Participants achieving a ≥50% reduction from baseline.")

scores %>% filter(timepoint == "baseline") %>%
  summarise(`Baseline MSSI = 0 (excluded from MSSI responder analysis)` = sum(mssi == 0)) %>%
  knitr::kable()
```

# Session information

```{r session}
sessionInfo()
```
